---
title: "Group 6 - Assignment 01"
output:
  html_document: default
  pdf_document: default
---

## Rania Karamallah | Sue Chen | Claire Tham 

### Assignment description

Data: 
We chose to look at police stations in relation to neighborhoods and open space in Boston. We wanted to examine the relationship between the location of police stations and green space. This spatial representation could possibly shed some light on the safety of green space and how the government prioritizes its resources. We included districts as well which can provide further insight into how the government distributes police stations throughout Boston. Potential areas of future research could include adding demographic data, crime data and how such statistics have changed over time.

Group Work: 
We were all eager to learn all aspects of this exercise, so we decided to do the exercise individually after we agreed on the data sets we would use. That helped us figure out the code and feel more confident about R interface. 

We each linked our rmd and html individual files to a Github Repo. and create an html format for our work. We had a few Zoom work sessions together that helped each one of us generate 5 different maps from the datasets we chose. 

For our submission as a group, we selected 5 maps from a collection of our individual maps. 

We would allocate 10 points to each member.

### packages
```{r load packages, message=FALSE}
library(sf)
library(tidyverse)
library(ggspatial)
library(ggthemes)

```

### datasets
```{r}
CommunityCenters <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/acedd06b39854088b0f2fefccffebf84_0.kml?outSR=%7B%22latestWkid%22%3A3857%2C%22wkid%22%3A102100%7D", quiet = TRUE)

Foodtrucks <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/437d8cb34b58481b9d7b07ea88912b0c_0.kml?outSR=%7B%22latestWkid%22%3A3857%2C%22wkid%22%3A102100%7D", quiet = TRUE)

Openspace <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/2868d370c55d4d458d4ae2224ef8cddd_7.kml", quiet = TRUE)

nhoods <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/3525b0ee6e6b427f9aab5d0a1d0a1a28_0.geojson?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D", quiet = TRUE)

policestation <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/e5a0066d38ac4e2abbc7918197a4f6af_6.kml?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D" , quiet= TRUE)
```


# Map 1

Comment: The base map does not show any details about the location and surrounding areas which makes it difficult to place the map within its context. The district outlines are very visible and clearly show the distinctions between different districts. The green space is very visible as well and is in a high-contrast color and is intuitively colored green. The police stations are difficult to read due to the size of the dots which is particularly problematic given that our goal is to visualize the placement of police stations in relation to the green space. We think that this is not the most successful map given that we could improve upon the visibility of the base map and the police stations.  

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartodark")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 1, shape = 23, alpha = 0.8, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, color = "gray", size = 0.1, 
          aes(fill = "Neighborhoods")) +
  scale_fill_manual(values = c("NA", "lightgreen"), name = "") +
  scale_color_manual(values = "orange", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```



# Map 2

Comment: We think that this is a successful map and this is our favorite map of the 5 maps. The base map shows sufficient information so as to contextualize the information for the reader and provide a sense of place but does not distract from the primary focus of the map which is the placement of the police stations in relation to the green space. The colors are complementary colors and contrast well with the base map. The color and shape of the police stations are very visible and the color "blue" is generally associated with police stations.

```{r message=FALSE}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartolight")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 3, shape = 15, alpha = 0.5, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, color = "black", size = 0.1, aes(fill =  "Neighborhoods")) +
  scale_fill_manual(values = c("NA", "lightgreen"), name = "") +
  scale_color_manual(values = "blue", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```


# Map 3

Comment: The color and shape that represents the police stations is not clear in this map as there is little contrast between the yellow and white background of the base map. The difficulty with reading this map arises from there being too much information and insufficient distinctions and a lack of a visual hierarchy directing the reader's eyes to the appropriate information within the map. For example, the red borders serve as a distraction given that the placement of the districts is not the primary focus of the map. 

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "stamenbw")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) + 
  geom_sf(data = nhoods, color = "red", size = 0.1, aes(fill = "Neighborhoods")) +
  geom_sf(data = policestation, size = 3, shape = 8, 
          aes(color = "Police Stations")) +
  scale_fill_manual(values = (c("NA", "lightgreen")), name = "") +
  scale_color_manual(values = "yellow", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))

```


# Map 4

Comment: The layout of this map removes the longitude and latitude lines which could be distracting to the reader and provide redundant information since the base map already includes labels and provides sufficient spatial context. This map shows police stations as large red dots, which connote a sense of danger rather than security. This highlights the accidental connotations or political stance of a map. Police stations, which could signal safety for some, are sources of danger for others. Although we did not set out to include this connotation in the map, we must be careful about what the reader can take away from it due to the stylistic choices chosen by the map-maker.

```{r}
ggplot() + annotation_map_tile(zoomin = 0, progress = "none", type = "hotstyle")  +
  geom_sf() +
  labs(caption = "Created by Group 6. Map tiles and data by OpenStreetMap")+ geom_sf(data = nhoods, color = NA, alpha = 0.5, aes(fill ="Neighborhoods")) + geom_sf(data = Openspace, color = NA, alpha = 0.5, aes(fill="Open Space")) + geom_sf(data = policestation, shape = 16, size = 5, aes(color = "Police Stations")) + scale_fill_manual(values = c("blue","green"), name = "") + scale_color_manual(values = "red", name = "")+ theme_void()

```


# Map 5

Comment: We think that this map is successful. The base map is not too noisy and fades into the background while providing the necessary context for the location of the map. The contrast between the blue and green makes the open space very prominent and easy to spot at first glance. The white boundaries serve to show the lines between neighborhoods in a clear way that does not distract from the other prominent information that the map is trying to convey. The police stations are indicated by small red symbols. We do think that the symbols could be more visible (for example if the lines could be thickened). We avoided the circular symbol as it denoted a certain radius/distance and we did not want to imply that we had data about walking distances from the police stations to the open space. 

```{r}
ggplot(nhoods) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "stamenbw")  +
  geom_sf(color = "white", size = 0.05, aes(fill = "Neighborhoods")) +
  geom_sf(data = Openspace, color = NA, size = 0.05, alpha = 1, 
          aes(fill = "Open Space")) + 
  geom_sf(data= policestation, color = "red", size= 3,  
          aes(shape = "Police Stations")) +  
  scale_fill_manual(values = c("blue", "green"), name = "") +
  scale_shape_manual(values = 7, name = "")
```



