---
title: "Group 6 - Assignment 01"
output:
  html_document: default
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
summary(cars)
```


```{r pressure, echo=FALSE}
plot(pressure)
```


```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Group 6: Rania Karamallah, Sue Chen, Claire Tham 

# Assignment discreption

Data: 
We chose to look at police stations in relation to neighborhoods and open space in Boston.

Group Work: 
We were all eager to learn all aspects of this exercise, so we decided to do the exercise individually after we agreed on the data sets we would use. That helped us figure out the code and feel more confident about R interface. 

We each linked our rmd and html individual files to a Github Repo. and create an html format for our work. We had a few Zoom work sessions together that helped each one of us generate 5 different maps from the datasets we chose. 

For our submission as a group, we selected 5 maps from a collection of our individual maps. In addition to these maps, each member of the group did the following:

Sue Chen: Created the Github Repo.
Rania Karamallah: Created the html file for the group assignment and wrote the design and work description.
Claire Tham: Submitted the assignment on behalf of the group

# loading packages
```{r load packages, message=FALSE}
library(sf)
library(tidyverse)
library(ggspatial)
library(ggthemes)

```

# loading datasets
```{r}
CommunityCenters <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/acedd06b39854088b0f2fefccffebf84_0.kml?outSR=%7B%22latestWkid%22%3A3857%2C%22wkid%22%3A102100%7D", quiet = TRUE)

Foodtrucks <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/437d8cb34b58481b9d7b07ea88912b0c_0.kml?outSR=%7B%22latestWkid%22%3A3857%2C%22wkid%22%3A102100%7D", quiet = TRUE)

Openspace <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/2868d370c55d4d458d4ae2224ef8cddd_7.kml", quiet = TRUE)

nhoods <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/3525b0ee6e6b427f9aab5d0a1d0a1a28_0.geojson?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D", quiet = TRUE)

policestation <- st_read("https://bostonopendata-boston.opendata.arcgis.com/datasets/e5a0066d38ac4e2abbc7918197a4f6af_6.kml?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D" , quiet= TRUE)
```


## Map 1

Comment: I think is is a successful map, the colors are easy to read with the background map.

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartodark")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 1, shape = 23, alpha = 0.8, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, fill = "NA", color = "gray", size = 0.1) +
  scale_fill_manual(values = "lightgreen", name = "") +
  scale_color_manual(values = "orange", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```



## Map 2

Comment: I think is is a successful map, the colors are easy to read with the background map.

```{r message=FALSE}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "cartolight")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 3, shape = 15, alpha = 0.5, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, fill = "NA", color = "black", size = 0.1) +
  scale_fill_manual(values = "lightgreen", name = "") +
  scale_color_manual(values = "blue", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```


## MAp 3

Comment: The color and shape that represents the police stations is not clear in this map as there is little contrast between the yellow and white bachground of the map.

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "stamenbw")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 3, shape = 8, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, fill = "NA", color = "red", size = 0.1) +
  scale_fill_manual(values = "lightgreen", name = "") +
  scale_color_manual(values = "yellow", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))

```


## Map 4

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "hotstyle")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 2, shape = 10, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, fill = "NA", color = "gray", size = 0.1) +
  scale_fill_manual(values = "red", name = "") +
  scale_color_manual(values = "black", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```


## Map 5

```{r}
ggplot(Openspace) +
  annotation_map_tile(zoomin = 0, progress = "none", type = "stamenwatercolor")  +
    geom_sf( size = 0.05, color = "darkgreen", 
          aes(fill =  "Open Space")) +
  geom_sf(data = policestation, size = 3, shape = 18, 
          aes(color = "Police Stations")) + 
  geom_sf(data = nhoods, fill = "NA", color = "white", size = 0.5) +
  scale_fill_manual(values = "black", name = "") +
  scale_color_manual(values = "purple", name = "") +
   theme(panel.background = element_rect(fill = "white"),
        legend.key = element_rect(fill = "white"))
```



